Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-12-18 ms.tex
gcm

\section{Atmospheric Composition}
Since the phase-resolved spectra are consistent with blackbodies (except for the Spitzer 4.5 $\mu$m broadband photometry point), we opted for a simple grid-based retrieval of the planet's atmospheric properties, similar to the grid search used in Mansfield et al. and Arcangeli et al. (in prep). We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation (\textbf{Mike: elaborate}). The forward models compute self-consistent, radiative-convective temperature-pressure (T-P) profiles, and the molecular abundances are calculated in each atmospheric layer assuming thermochemical equilibrium.  We included opacity from the major absorbers expected for a hot Jupiter atmosphere (FIXME: Mike, what molecules are included?). Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates (FIXME: what temperatures?).  Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite.  We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13} (FIXME: elaborate).

@@

\section{Comparison with GCMs}

@@

>>>>

\section{Atmospheric Composition}
Since the phase-resolved spectra are consistent with blackbodies (except for the Spitzer 4.5 $\mu$m broadband photometry point), we opted for a simple grid-based retrieval of the planet's atmospheric properties, similar to the grid search used in Mansfield et al. and Arcangeli et al. (in prep). We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation (\textbf{Mike: elaborate}). The forward models compute self-consistent, radiative-convective temperature-pressure (T-P) profiles, and the molecular abundances are calculated in each atmospheric layer assuming thermochemical equilibrium.  We included opacity from the major absorbers expected for a hot Jupiter atmosphere (FIXME: Mike, what molecules are included?). Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates (FIXME: what temperatures?).  We Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite.  We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13} (FIXME: elaborate).

@@

\section{Comparison with GCMs}
To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra. We used the SPARC

@@

There are many factors contributing to the blackbody spectra --
weak water xsec contrast, isothermal pt, H-, and dissociated water
